Estimate_M2

### 2024-11-23 draftdesresults.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Draft Result Descriptives"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

@@

</html>

@@

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

## Network Description

@@

### Nr. of nodes/vertices

@@

### Nr. of edges

@@

### Dyad census

@@

### Triad-census

@@

-->
```
### Edge-density

@@

### more in depth:

````{=html}
<!--

#### reciprocity

```{r recip}
reciprocity(test_w1, ignore.loops = TRUE, mode = c("default", "ratio"))
```

-->
````

#### Degree centrality

@@

#### Betweenness Centrality

@@

#### Clustering

@@

# Network-level descriptives

## x. Average path length

```{r path length}
mean((ego_size(test_w1, order = 2, mode = "out") - 1)/vcount(test_w1))
```

## STILL DO! Segregation - Mortons I - also graphs below

**STILL DO!**

# Plotting:

## Plots WITH isolates 
###Gender 
#### whole network
```{r plot gender}

plot(test_w1,
     vertex.color = ifelse(df_ego$gender == 1, "#FFED6F", "#80B1D3"), # now, I can use actor attributes for plotting.
# here: if gender = 1 (aka man) then red dot, if not then blue 
  vertex.label = NA,
  vertex.size = 7.5,
  edge.width = 0.5,
  edge.arrow.size = 0.1,
  main = "Network with isolates [yellow = female, blue = male]",)

#### per department

```{r with iso gender per dep old code }

indegr_w1 <- degree(test_w1, mode = "in")

# assign gender to scholar
V(test_w1)$gender <- df_ego$gender

# assign discipline to scholar
V(test_w1)$discipline <- df_ego$discipline.24

V(test_w1)$indegree <- indegr_w1

p_gender <- ggraph(test_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
    color = as.factor(discipline), shape = as.factor(gender))) + scale_size(range = c(3, 10)) + theme_void() +  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_gender + labs(title = "Departments with isolates", subtitle = "Plot of indegree and gender", caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
```

### H-Index 
#### whole network 
```{r  h ind with iso old code }
indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

# set size of plot
options(repr.plot.width = 15, repr.plot.height = 18)

# plot wave 1 with isolates
p_iso <- ggraph(test_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.3, arrow = arrow(length = unit(1, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
    color = h_index)) + scale_size(range = c(3, 10)) +
  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
  theme_void() +
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
    )

p_iso + labs(title = "Network with isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to: Scholars RU sociology and political science departments") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold"), plot.subtitle = element_text(hjust = 0.5),
        plot.caption = element_text(hjust = 1))
```

### H-Index and Gender
#### whole network 
```{r dark g&h with iso}
indegr_w1 <- degree(test_w1, mode = "in")

#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender
# V(test_w1)$gender <- ifelse(df_ego$gender >= 0.5,1,0)

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

p_gender <- ggraph(test_w1,
  layout = "fr") +
  geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.3, arrow = arrow(length = unit(1, "mm"), type = "closed")) +  # Darker edge color
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
  theme_void() +
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_gender + 
  labs(title = "Network with isolates",
    subtitle = "Plot of indegree, H-index and gender",
    caption = "Gender: 0 = female, 1 = male.\nData refer to: Scholars RU sociology and political science departments.") +
  theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))

---

## Plots WITHOUT isolates 
The isolates of the network have been removed to allow for a better readability of the graphs. Only vertices with edges remain part of the visualizations. In other words, only scholars with collaborations are seen in the following graphs.

```{r removing isolates}
indegr_w1 <- igraph::degree(test_w1, mode = "in")

isolates_w1 <- V(test_w1)[degree(test_w1, mode = "all") == 0]

noisolates_w1 <- delete_vertices(test_w1, isolates_w1)

gsize(noisolates_w1) # edges
gorder(noisolates_w1) # vertices 
```

### Gender 
#### DESCIP<> whole network

```{r plot wo isolates}
plot(noisolates_w1,
  vertex.color = ifelse(df_ego$gender == 1, "#80B1D3", "#FFED6F"), # now, I can use actor attributes for plotting.
  # here: if gender = 1 (aka man) then red dot, if not then blue 
  vertex.label = NA,
  vertex.size = 9,
  vertex.frame.color = "black",
  edge.curved = 0.1,
  edge.arrow.size = 0.5,
  edge.color = "#999999",
  edge.width = 0.5,
  main = "Network without isolates [yellow = female, blue = male]",
  asp=0)
```
#### RESULTS <> indegree & department

```{r without iso gender per dep old code}
# assign gender to scholar
V(test_w1)$gender <- df_ego$gender

# assign disciplines to scholars
V(test_w1)$discipline <- df_ego$discipline.24
V(test_w1)$indegree <- indegr_w1

# remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

p_noisgender <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm")), type = "closed") +
    geom_node_point(aes(size = indegree, color = as.factor(discipline), shape = as.factor(gender))) +
    scale_size(range = c(3, 10)) + theme_void() +   theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_noisgender + labs(title = "Departments without isolates", subtitle = "Plot of indegree and gender",
    caption = "Gender: 0 = female, 1 = male.\n Data refer to scholars from Radboud University.") + theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
```

### H-index 
#### RESULTS<> Whole network (indegree)
```{r}
indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

# remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

# set size of plot
options(repr.plot.width = 15, repr.plot.height = 15)

# plot wave 1 without isolates
p_noiso <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(3, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
    color = h_index)) + scale_size(range = c(3, 10)) + scale_color_gradient(low = "red", high = "blue") +
    theme_void() +   theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_noiso + labs(title = "Network without isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to: Scholars RU sociology and political science departments") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
```

#### per department
```{r hind without iso old code}
indegr_w1 <- degree(test_w1, mode = "in")

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
# assign discipline to scholar
V(test_w1)$discipline <- df_ego$discipline.24

V(test_w1)$indegree <- indegr_w1

# remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

# set size of plot
options(repr.plot.width = 15, repr.plot.height = 15)

# plot wave 1 without isolates
p_noiso <- ggraph(noisolates_w1, layout = "fr") + geom_edge_link(end_cap = circle(4, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(2, "mm"), type = "closed")) + geom_node_point(aes(size = indegree,
    color = h_index, shape = as.factor(discipline))) + scale_size(range = c(3, 10)) + scale_color_gradient(low = "red",
    high = "blue") + theme_void() +   theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_noiso + labs(title = "Departments without isolates", subtitle = "Plot of indegree and H-index", caption = "Data refer to scholars from Radboud University.") +
    theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))
```

### RESULTS <> H-index AND Gender (indegree)

```{r dark g&h without iso}
#assign gender to scholar 
V(test_w1)$gender <- df_ego$gender

# assign h-index to scholar
V(test_w1)$h_index <- df_ego$h_index
V(test_w1)$indegree <- indegr_w1

#remove isolates
noisolates_w1 <- delete_vertices(test_w1, V(test_w1)[degree(test_w1) == 0])

p_noisogender <- ggraph(noisolates_w1,
  layout = "fr") +
  geom_edge_link(end_cap = circle(3, 'mm'),color = "#D9D9D9", width = 0.7, arrow = arrow(length = unit(1.75, "mm"), type = "closed")) +  # Darker edge color
  geom_node_point(aes(size = indegree, color = h_index, shape = as.factor(gender))) +   
  scale_size(range = c(3, 10)) + 
  scale_color_gradient(low = "#F6222E", high = "#3283FE") +  # Retain original gradient
  theme_void() +
  theme(
    plot.background = element_rect(fill = "#2d2d2d", color = NA),  # Dark background
    panel.background = element_rect(fill = "#2d2d2d", color = NA),
    text = element_text(color = "#f0f0f0")  # White text
  )

p_noisogender + labs(title = "Network without isolates",
        subtitle = "Plot of indegree, H-index and gender",
        caption = "Gender: 0 = female, 1 = male.\n Data refer to: Scholars RU sociology and political science departments.") +   
  theme(plot.title = element_text(hjust = 0.5, face = "bold", color = "#f0f0f0"), plot.subtitle = element_text(hjust = 0.5, color = "#f0f0f0"), plot.caption = element_text(hjust = 1, color = "#f0f0f0"))

>>>>

---
title: "Descriptive Results"
author: "Verooo"
date: "2024-11-23"
output: html_document
---

@@

</html>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

@@

# Network Description

@@

## Nr. of nodes/vertices

@@

## Nr. of edges

@@

## Dyad census

@@

## Triad-census

@@

-->
```
## Edge-density

@@

## Degree centrality

@@

## Betweenness Centrality

@@

## Clustering

@@

## Segregation ?

# Plots

### 2024-11-23 drafttheory.Rmd
modelestimates-GOFs-desresults-darkgraph

-   ***H3**: Gender homophily is less influential in collaboration decisions when the potential collaborator has a high level of academic prestige (e.g., a strong publication record in high-prestige journals).*

This hypothesis posits that prestige serves as a countervailing force to homophily. Collaboration with high-prestige individuals is a strategic choice, driven by the potential for increased visibility and career advancement, which may diminish the salience of gender in collaboration decisions.

>>>>

-   ***H3**: Gender homophily is less influential in collaboration decisions when the potential collaborator has a higher Hirsch-Index.*

This hypothesis posits that prestige (higher h-index) serves as a countervailing force to homophily. Collaboration with high-prestige individuals is a strategic choice, driven by the potential for increased visibility and career advancement, which may diminish the salience of gender in collaboration decisions.

### 2024-11-23 estimate_M0.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "RSienatry"
author: "Verooo"
date: "2024-11-08"
output: html_document
---
```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

```{r klippy, echo=FALSE, include=FALSE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Getting started

```{r clean}
rm(list = ls())

@@

@@

## More functions

@@

## Load data

```{r data}
scholars <- fload("./data/processed/scholars_20240924.rda") #make sure to lead fload first ofcourse
```

@@

test  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = c("sociology", "political science"),
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("all")) # all, first, last # which ties in there

# USE not all but first or last so the ties are directed from "perspective" of first author of the publications 
# usually first most prestige

@@

## Step 1: Define data
```{r RSiena}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

#put diagonals to zero 
diag(wave1) <- 0
diag(wave2) <- 0
# we want a binary tie (not a weighted tie)
wave1[wave1 > 1] <- 1
wave2[wave2 > 1] <- 1
```

```{r RSiena define 1}
# put the nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))
#dependent
nets <- sienaDependent(net_array)
```

```{r RSiena define 2}

df_ego <- fload("./data/processed/df_ego_20241108.rda") #make sure to lead fload first ofcourse

#put gender in object 
gender <- df_ego$gender
#covariate
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

#put h-index in object 
h_index <- df_ego$h_index
df_ego$h_index
#covarite 2
h_index_RS <- coCovar(h_index) # h_index as covariate in RSiena

#define data 
mydata <- sienaDataCreate(nets, gender_RS, h_index_RS)

@@

## Step 2: Make effects structure 
```{r RSiena myeff}
#define effects structure 
myeff <- getEffects(mydata)

@@

## Step 3: initial description (skipped)
Nothing for now. :)

## Step 4: Specify model 
```{r RSiena spec mod}

myeff <- includeEffects(myeff, isolateNet, inPop, outAct)

myeff <- includeEffects(myeff, egoX, altX, sameX, interaction1 = "gender_RS")
#include effect of h index later too etc
#look up which effects to iclude

myAlgorithm <- sienaAlgorithmCreate(modelType = c(nets=6), projname = "proProject")
# undirected: model 6 "additive model", #check manual for this
```

## Step 5: Estimate model 
```{r RSiena-model estimate, eval = FALSE}
# estimate the model 
model1 <- siena07(myAlgorithm, data = mydata, effects = myeff, returnDeps = TRUE)
#latter needed for GOF

model1

# output:  convergence ration NA probably bc we chose all ties to be included (type = "all") earlier
# we can go back and change that or change it here in the myAlgorithm function

# Make it a directed network 
# focus: writing, 
# model interpretation

@@

>>>>

---
title: "Estimate_M0"
author: "Verooo"
date: "2024-11-22"
output: html_document
---

<html lang="en">
<head>
    <meta charset="UTF-8">
    <meta name="viewport" content="width=device-width, initial-scale=1.0">
    <title>My Descriptives</title>
    <link rel="stylesheet" href="styles.css">  <!-- Link to the CSS file I created for dark mode code chunks -->

</head>
</html>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, globalsettings, echo=FALSE, warning=FALSE, results='hide'}
library(knitr)

@@

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position = c('top', 'right'))
#klippy::klippy(color = 'darkred')
#klippy::klippy(tooltip_message = 'Click to copy', tooltip_success = 'Done')
```

NULL MODEL
Testing if the models can be estimated in separate files without error. Easier for me than cleanign the workspace due to oversight of having separate tabs. Of course I still clean the workspace in between but yaknow. Visual distinction.

# Setup
Clean workspace
```{r clean}
rm(list = ls())
```

@@

Functions chunk

@@

More functions

@@

GOF auxiliary Functions 
<!--
# see here: ?'sienaGOF-auxiliary'

# The geodesic distribution is not available from within RSiena, and therefore is copied from the
# help page of sienaGOF-auxiliary:

# GeodesicDistribution calculates the distribution of non-directed geodesic distances; see
# ?sna::geodist The default for \code{levls} reflects the usual phenomenon that geodesic distances
# larger than 5 do not differ appreciably with respect to interpretation.  Note that the levels of
# the result are named; these names are used in the \code{plot} method.

-->
[unsure if needed. put these here when trying to figure out why sienaGOF function does not work.]
```{r}

GeodesicDistribution <- function(i, data, sims, period, groupName, varName, levls = c(1:5, Inf), cumulative = TRUE,
    ...) {
    x <- networkExtraction(i, data, sims, period, groupName, varName)
    require(sna)
    a <- sna::geodist(symmetrize(x))$gdist
    if (cumulative) {
        gdi <- sapply(levls, function(i) {
            sum(a <= i)
        })
    } else {
        gdi <- sapply(levls, function(i) {
            sum(a == i)
        })
    }
    names(gdi) <- as.character(levls)
    gdi
}

# The following function is taken from the help page for sienaTest

testall <- function(ans) {
    for (i in which(ans$test)) {
        sct <- score.Test(ans, i)
        cat(ans$requestedEffects$effectName[i], "\n")
        print(sct)
    }
    invisible(score.Test(ans))
}
```

# Get Data

## Load Scholar Data

```{r scholar data}
scholars <- fload("./data/processed/scholars_20240924.rda") 
#make sure to lead fload first of course
```

Save the output of the function.

@@

test  <- fcolnet(data = scholars, 
                university = "RU", 
                discipline = c("sociology", "political science"),
                waves = list(c(2015, 2018), c(2019, 2023)), 
                type = c("first"))

@@

## Load Ego Data

```{r df_ego data, include= FALSE}
df_ego <- fload("./data/processed/df_ego_20241108.rda")

@@

# Make Network Data

```{r RSiena network data}
#step1 data
wave1 <- test$nets[1,,]
wave2 <- test$nets[2,,]

# put nets in an array
net_array <- array(data = c(wave1, wave2), dim = c(dim(wave1), 2))

@@

## Model 0 - Null Model

**CHANGE** First, I estimate a null model with only reciprocity and
degree. It has a convergence of NUMBER and a Goodness of Fit on the
indegree distribution of 0 (**NUMBER BEOFRE**), indicating that the model
fits the data very badly. This makes sense, given that the model does
not include any network statistics. Both reciprocity and density are
significant for an alpha of NUMBER. It is important to mention that
significance in RSiena means something different than in conventional
statistics. In normal statistics, such as OLS-regression, significance
of estimates refers to the fact that they are not 0 (RELEVANT?). In
RSiena, however, it refers to the fact that the estimates were precisely
determined (Ripley et al. 2011). Going forward with this chapter,
significance will refer to this definition of significance. The density
parameter has a value of NUMBER, which means that people generally do
not want to have a dense network. The reciprocity parameter has a value
of NUMBER, which means that people like to send ties back to people who
have sent a tie to them.

5.1.1 Create SienaData

### Step 1: Define Siena Data & Variables

```{r RSiena define m0}
# dependent variable 
nets <- sienaDependent(net_array)

# define data object 
mydata_M0 <- sienaDataCreate(nets)

@@

Print short descriptive report

```{r}
ifelse(!dir.exists("results"), dir.create("results"), FALSE)

#if there is not a folder called "results" in your repository: make one

```{r}
print01Report(mydata_M0, modelname = "./results/results_M0") # create file with report in results folder 
```

### Step 2: Make effects object/structure

```{r RSiena myeff M0}
# define effects structure 
myeff_M0 <- getEffects(mydata_M0)

### Step 3: Add Effects

```{r effects M0}
# Null model: just myeff (just degree and reciprocity by default) # model0  #for this when you create Siena Data, do not add the gender variable

myeff_M0 <- includeEffects(myeff_M0, isolateNet, inPop, outAct)

### Step 4: Specify model/algorithm

```{r algo M0}

myAlgorithm_M0 <- sienaAlgorithmCreate (projname = "results_M0")

### Step 5: Estimate model

```{r estimate M0, eval=FALSE}

# estimate the model 
Model0 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, returnDeps = TRUE)

Model0
# maximum convergence >.25

# run again:
Model0.1 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, prevAns= Model0, returnDeps = TRUE)

Model0.1

# fsave(Model0, file ="estimated_M0")
# fsave(Model0.1, file = "estimated_M0.1")

```{r load M0 output, echo=FALSE}
Model0 <- fload("./data/processed/estimated_M0_20241123.rda")
Model0

Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
Model0.1

### Step 6: GOF - Goodness of Fit

```{r GOF M0}
GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M0.1, main = 'GOF - "Null" Model 0.1 \n Indegree Distribution')
```

### 2024-11-23 estimate_M1.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Estimate_M0"
author: "Verooo"
date: "2024-11-22"
output: html_document
---

@@

NULL MODEL
Testing if the models can be estimated in separate files without error. Easier for me than cleanign the workspace due to oversight of having separate tabs. Of course I still clean the workspace in between but yaknow. Visual distinction.

# Setup
Clean workspace
```{r clean}
rm(list = ls())
```

@@

@@

## Model 0 - Null Model

**CHANGE** First, I estimate a null model with only reciprocity and
degree. It has a convergence of NUMBER and a Goodness of Fit on the
indegree distribution of 0 (**NUMBER BEOFRE**), indicating that the model
fits the data very badly. This makes sense, given that the model does
not include any network statistics. Both reciprocity and density are
significant for an alpha of NUMBER. It is important to mention that
significance in RSiena means something different than in conventional
statistics. In normal statistics, such as OLS-regression, significance
of estimates refers to the fact that they are not 0 (RELEVANT?). In
RSiena, however, it refers to the fact that the estimates were precisely
determined (Ripley et al. 2011). Going forward with this chapter,
significance will refer to this definition of significance. The density
parameter has a value of NUMBER, which means that people generally do
not want to have a dense network. The reciprocity parameter has a value
of NUMBER, which means that people like to send ties back to people who
have sent a tie to them.

5.1.1 Create SienaData

@@

```{r RSiena define m0}
# dependent variable 
nets <- sienaDependent(net_array)

# define data object 
mydata_M0 <- sienaDataCreate(nets)

@@

```{r}
print01Report(mydata_M0, modelname = "./results/results_M0") # create file with report in results folder 
```

@@

```{r RSiena myeff M0}
# define effects structure 
myeff_M0 <- getEffects(mydata_M0)

@@

```{r effects M0}
# Null model: just myeff (just degree and reciprocity by default) # model0  #for this when you create Siena Data, do not add the gender variable

myeff_M0 <- includeEffects(myeff_M0, isolateNet, inPop, outAct)

@@

```{r algo M0}

myAlgorithm_M0 <- sienaAlgorithmCreate (projname = "results_M0")

@@

```{r estimate M0, eval=FALSE}

# estimate the model 
Model0 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, returnDeps = TRUE)

Model0
# maximum convergence >.25

# run again:
Model0.1 <- siena07(myAlgorithm_M0, data = mydata_M0, effects = myeff_M0, prevAns= Model0, returnDeps = TRUE)

Model0.1

# fsave(Model0, file ="estimated_M0")
# fsave(Model0.1, file = "estimated_M0.1")

```{r load M0 output, echo=FALSE}
Model0 <- fload("./data/processed/estimated_M0_20241123.rda")
Model0

Model0.1 <- fload("./data/processed/estimated_M0.1_20241123.rda")
Model0.1

@@

```{r GOF M0}
GOF_M0.1 <- sienaGOF(Model0.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M0.1, main = 'GOF - "Null" Model 0.1 \n Indegree Distribution')
```

>>>>

---
title: "Estimate_M1"
author: "Verooo"
date: "2024-11-22"
output: html_document
---

@@

# Setup
Clean workspace. 
```{r clean}
rm(list = ls())
```

@@

MODEL 1
Testing if the models can be estimated in separate files without error. Easier for me than cleanign the workspace due to oversight of having separate tabs. Of course I still clean the workspace in between but yaknow. Visual distinction.

@@

## Model 1 - Structural Effects

**CHANGE** This model includes the relevant network statistics: InPop,
outAct, isolateNet.

It has a convergence of NUMBER and a Goodness of Fit on the indegree
distribution of NUMBER.

Indegree Popularity (inPop) is defined as the extent to which people who
have a lot of indegrees are more popular to connect with. This parameter
is NUMBER, meaning that actors have a preference to connect with actors
who have a lot of indegrees. The parameter is significant for an alpha
of NUMBER.

Outdegree Activity (outAct) has a value of NUMBER, but is not
significant. IsolateNet is significant andhas a value of NUMBER and
refers to the preference of remaining an isolate. As this value is
positive (IS IT??!), it means that people prefer to be an isolate in the
network.

@@

```{r RSiena define M1}
# dependent variable 
nets <- sienaDependent(net_array)

# define data object 
mydata_M1 <- sienaDataCreate(nets)

@@

```{r}
print01Report(mydata_M1, modelname = "./results/results_M1") # create file with report in results folder 
```

@@

```{r RSiena myeff m1}
# define effects structure 
myeff_M1 <- getEffects(mydata_M1)

@@

```{r effects m1}
myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)

@@

```{r algo m1}

myAlgorithm_M1 <- sienaAlgorithmCreate (projname = "results_M1")

@@

```{r estimate m1}
# estimate the model 
Model1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, returnDeps = TRUE)
#latter needed for GOF

Model1

Model1.1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, prevAns =Model1, returnDeps = TRUE)
#latter needed for GOF 
Model1.1

@@

```{r GOF M1}
GOF_M1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M1, main = "GOF - Model 1 \n Indegree Distribution")
```

### 2024-11-23 estimate_M2.Rmd
modelestimates-GOFs-desresults-darkgraph

---
title: "Estimate_M1"
author: "Verooo"
date: "2024-11-22"
output: html_document
---

@@

# Setup
Clean workspace. 
```{r clean}
rm(list = ls())
```

@@

MODEL 1
Testing if the models can be estimated in separate files without error. Easier for me than cleanign the workspace due to oversight of having separate tabs. Of course I still clean the workspace in between but yaknow. Visual distinction.

@@

## Model 1 - Structural Effects

**CHANGE** This model includes the relevant network statistics: InPop,
outAct, isolateNet.

It has a convergence of NUMBER and a Goodness of Fit on the indegree
distribution of NUMBER.

Indegree Popularity (inPop) is defined as the extent to which people who
have a lot of indegrees are more popular to connect with. This parameter
is NUMBER, meaning that actors have a preference to connect with actors
who have a lot of indegrees. The parameter is significant for an alpha
of NUMBER.

Outdegree Activity (outAct) has a value of NUMBER, but is not
significant. IsolateNet is significant andhas a value of NUMBER and
refers to the preference of remaining an isolate. As this value is
positive (IS IT??!), it means that people prefer to be an isolate in the
network.

@@

```{r RSiena define M1}
# dependent variable 
nets <- sienaDependent(net_array)

# define data object 
mydata_M1 <- sienaDataCreate(nets)

@@

```{r}
print01Report(mydata_M1, modelname = "./results/results_M1") # create file with report in results folder 
```

@@

```{r RSiena myeff m1}
# define effects structure 
myeff_M1 <- getEffects(mydata_M1)

@@

```{r effects m1}
myeff_M1 <- includeEffects(myeff_M1, isolateNet, inPop, outAct)

@@

```{r algo m1}

myAlgorithm_M1 <- sienaAlgorithmCreate (projname = "results_M1")

@@

```{r estimate m1}
# estimate the model 
Model1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, returnDeps = TRUE)
#latter needed for GOF

Model1

Model1.1 <- siena07(myAlgorithm_M1, data = mydata_M1, effects = myeff_M1, prevAns =Model1, returnDeps = TRUE)
#latter needed for GOF 
Model1.1

@@

```{r GOF M1}
GOF_M1 <- sienaGOF(Model1.1, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M1, main = "GOF - Model 1 \n Indegree Distribution")
```

>>>>

---
title: "Estimate_M2"
author: "Verooo"
date: "2024-11-22"
output: html_document
---

@@

MODEL 2
Testing if the models can be estimated in separate files without error. Easier for me than cleanign the workspace due to oversight of having separate tabs. Of course I still clean the workspace in between but yaknow. Visual distinction.

# Setup
clean workspace
```{r clean}
rm(list = ls())
```

@@

@@

## Model 2 - Gender

**CHANGE** Model 2 builds on Model 1 and includes the network statistics
for gender: diffX, diffXTransTrip, egoX & altX. This model has a
convergence of 0.23 and a Goodness of Fit on the indegree distribution
of 0.184. For the structural network statistics we find similar results,
in terms of estimate size and significance, as in Model 1. However, the
outdegree activity parameter almost reaches significance (-1.7135484).
With regard to the covariate network statistics, we find that the gender
of ego (egoX), the gender of alter (altX) and the difference between ego
and alter (diffX) is not significant and thus the estimate cannot be
trusted. The transtrip for different gender (diffXTransTrip) is positive
and significant, which implies that an ego prefers to close triads with
alters who have a different gender score than theirs. This is an
interesting finding, because it implies that their is a tendency towards
diverse collaboration. However, when compared to the level of gender
clustering and the fact that this clustering decreased, this finding
does make sense.

@@

```{r RSiena define m2}
# dependent variable 
nets <- sienaDependent(net_array)

# put gender in object 
gender <- df_ego$gender

# covariate 1
gender_RS <- coCovar(gender) # gender as covariate in Rsiena

# define data object 
mydata_M2 <- sienaDataCreate(nets, gender_RS)

@@

```{r}
print01Report(mydata_M2, modelname = "./results/results_M2") # create file with report in results folder 
```

@@

```{r RSiena myeff m2}
# define effects structure 
myeff_M2 <- getEffects(mydata_M2)

@@

```{r effects m2}
myeff_M2 <- includeEffects(myeff_M2, isolateNet, inPop, outAct)

myeff_M2 <- includeEffects(myeff_M2, egoX, altX, sameX, interaction1 = "gender_RS")

@@

```{r algo m2}

myAlgorithm_M2 <- sienaAlgorithmCreate (projname = "results_M2")

@@

```{r estimate m2}
# estimate the model 
Model2 <- siena07(myAlgorithm_M2, data = mydata_M2, effects = myeff_M2, returnDeps = TRUE)
#latter needed for GOF

Model2

@@

```{r GOF M2}
GOF_M2 <- sienaGOF(Model2, IndegreeDistribution, verbose = FALSE, join = TRUE, varName = "nets")

plot(GOF_M2, main = "GOF - Model 2 \n Indegree Distribution")
```
